A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-07-29 papers/paper1/ms.tex

% \begin{figure}[hbt!]
%   \includegraphics[width=0.95\textwidth]{figures/contrast_spectrum2.pdf}
%   \caption{Illustration of starspot contrast as seen in \tess\ and \kepler. The red shaded spectrum illustrates the contrast for an M0V spectral type for a choice of spot and ambient photospheric temperatures. The thick blue left-most curve illustrates the \kepler\ passband, the thick green line to its right illustrates the \tess\ passband centered near 850 nm.  A lower number means darker spots.}
%   \label{fig:filtercurve}
% \end{figure}

>>>>

\begin{figure}[hbt!]
  \includegraphics[width=0.95\textwidth]{figures/contrast_spectrum2.pdf}
  \caption{Illustration of starspot contrast as seen in \tess\ and \kepler. The red shaded spectrum illustrates the contrast for an M0V spectral type for a choice of spot and ambient photospheric temperatures. The thick blue left-most curve illustrates the \kepler\ passband, the thick green line to its right illustrates the \tess\ passband centered near 850 nm.  A lower number means darker spots.  }
  \label{fig:filtercurve}
\end{figure}
